Spatial Reasoning and Data Displays

### 2015-02-06 Paper/Draft1/TestingVisualAptitude.Rnw
discussion of fig 6

\newtext{For input variables $X_i$, $i=1, ..., K$ and output components $PC_j$, $j=1, ..., K$, the rotation matrix, $M$ has dimension $K\times K$ (indexed by $i$ and $j$ respectively), and the importance vector $I$ has dimension $1\times K$ (indexed by $j$). For each $X_i$ and $PC_j$, we define the influence of variable $X_i$ on component $PC_j$ as follows:
}

@@

The influence is a measure of the contribution of an input variable to the principal component, scaled by the importance of that principal component to the overall variability in the data.

>>>>

\newtext{For variables $X_i$, $i=1, ..., K$ a principal component analysis results in a set of $K$ principal  components $PC_j$, $j=1, ..., K$, given as the rows of the rotation matrix, $M$ (which has dimension $K\times K$, indexed by $i$ and $j$ respectively).

The importance $I_j$ of each component is determined by the amount of variability the data exhibits along each of the principal axis.

The influence of variable $X_i$ on component $PC_j$ is then defined as:
}

@@

\comment{Sign of influence? Influence is the smallest, if it is zero. The sign is kept to show separation between variables. You still need to comment on that.}
Influence is therefore a measure of the contribution of an input variable to the principal component, scaled by the importance of that principal component to the overall variability in the data.
